Models

### 2023-02-21 Code/Models.Rmd
Small changes

```{r}
library(clusrank)
#t.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
#clusWilcox.test(comp$Time, group=comp$Group, cluster=comp$Cluster, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, paired = TRUE, alternative = "greater", method = "ds", data = comp)
clusWilcox.test(Time, cluster = Athlete, paired = TRUE, alternative = "greater", method = "rgl", data = comp)
#wilcox.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
```

```{}
Cluster by 2019 and 2022
Columns: Athlete, RxnTime, 2019/2022
```

```{r}
nations <- read.csv("../Data/ClusrankNatvsWorld.csv")
colnames(nations) <- c("Time", "Group", "Cluster")
```

```{r}
library(clusrank)
#t.test(nations$NatH, nations$WorldH, paired = TRUE)
#clusWilcox.test(nations$Time, group=nations$Group, cluster=nations$Cluster,
                #paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(nations$Time, group=nations$Cluster, cluster = nations$Group, 
                paired = TRUE, alternative = "greater", method = "ds")
#wilcox.test(nations$NatH, nations$WorldH, paired = TRUE)
```

>>>>

```{}
One thing that we discovered is that including group=Year does not effect the the z score or p value.  Changing the method from
rgl to ds does effect z score.
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, cluster = Athlete, data = comp, paired = TRUE, alternative = "greater", method = "rgl")
```

```{r}
nations <- read.csv("../Data/ClusrankNatvsWorld.csv")
colnames(nations) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, paired = TRUE, alternative = "greater", method = "rgl")
```

```{r}
In both examples, rgl produced a smaller p value
```
